Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-21 methods-and-results.Rmd
feature extraction added

Our selection: density, inertia, instability, diversity \citep[][]{dejonckheere2019, kuppens2017}

\begin{itemize}
  \item 
\end{itemize}

@@

\begin{itemize}
  \item dimension reduction
  \item feature selection
  \begin{itemize}
    \item filter: evaluate individual features' impact / importance / relevance. Univariate (ranking-based) or multivariate (preferred bc. can handle redundant and irrelevant features)
    \begin{itemize}
      \item unvariate, often based on information or spectral analysis (univariate inclusion test \citep[i.e., alpha-corrected t-tests][]{christ2018})
    \end{itemize}
    \item wrapper: search problem --- compare different models based on evaluation criterion (i.e., model performance; e.g., $R^2$, accuracy, ...). "high computational cost, and they are limited to be used in conjunction with a particular clustering algorithm."
    \begin{itemize}
      \item Exhaustive Feature Selection (i.e., brute force)
      \item forward selection (e.g., greedy Forward Search \citep[][]{wang2006})
      \item backward elimination
      \item Bi-directional elimination (Stepwise Selection)
    \end{itemize}
    \item hybrid: (usually) first filter then wrapper (e.g., Bayesian Filter KMeans)
    \item [embedded: feature selection as part of the model construction process. E.g., LASSO Regularization L1, or Random Forest Importance] MOSTLY FOR SUPERVISED / LABELED DATA (e.g., regressions)
  \end{itemize}
\end{itemize}

>>>>

Our selection based on describing time series aspects relevant to human experiences \citep[density, inertia, instability, diversity;][]{dejonckheere2019, kuppens2017}

\begin{itemize}
  \item diversity: multiple variables
  \begin{itemize}
    \item field and concept specific: affect, behavior, cognition, desire
  \end{itemize}
  \item (in)stability
  \begin{itemize}
    \item mean of sum squared differences
    \item mean absolute change
  \end{itemize}
  \item central tendency
  \begin{itemize}
    \item mean
    \item median
  \end{itemize}
  \item variance
  \begin{itemize}
    \item variance / standard deviation
    \item median absolute distance
    \item (range / min + max)
    \item (change in SD)
    \item (variation coefficient (SE/mean))
  \end{itemize}
  \item inertia
  \begin{itemize}
    \item autocorrelation (lag-1)
    \item (additional periodicity/seasonality (e.g., day, week))
  \end{itemize}
  \item linear trend
  \begin{itemize}
    \item OLS regression slope
  \end{itemize}
  \item nonlinear trend
  \begin{itemize}
    \item GAM spline coefficient: estimated degrees of freedom (edf; how wiggly the line is)
    \item (number of spikes \citep[e.g.,][]{caro-martin2018})
    \item (Fourier Transform Coefficients (representation in square- and sine waves))
    \item (polynomial coefficients (Langevin model))
    \item (semi-markov model parameters)
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item dimension reduction
  \item feature selection
  \begin{itemize}
    \item filter: evaluate individual features' impact / importance / relevance. Univariate (ranking-based) or multivariate (preferred bc. can handle redundant and irrelevant features)
    \begin{itemize}
      \item unvariate, often based on information or spectral analysis (univariate inclusion test \citep[i.e., alpha-corrected t-tests][]{christ2018})
    \end{itemize}
    \item wrapper: search problem --- compare different models based on evaluation criterion (i.e., model performance; e.g., $R^2$, accuracy, ...). "high computational cost, and they are limited to be used in conjunction with a particular clustering algorithm."
    \begin{itemize}
      \item Exhaustive Feature Selection (i.e., brute force)
      \item forward selection (e.g., greedy Forward Search \citep[][]{wang2006})
      \item backward elimination
      \item Bi-directional elimination (Stepwise Selection)
    \end{itemize}
    \item hybrid: (usually) first filter then wrapper (e.g., Bayesian Filter KMeans)
    \item (embedded: feature selection as part of the model construction process. E.g., LASSO Regularization L1, or Random Forest Importance) MOSTLY FOR SUPERVISED / LABELED DATA (e.g., regressions)
  \end{itemize}
\end{itemize}
